---
output:
  pdf_document: default
  word_document: default
  html_document: default
---

#HYPOTHESES TESTING

"This document provides an information to houses sold in City of Melbourne . It includes all the details of the different types of houses sold in different years . We have used the variable name as 'housing.dataset' in order to read our csv file and store in the dataframe . We will use different variables for Hypotheses Testing."

#------------------------------------------------------------------------------------

#Introduction
The Housing dataset consist of eight attributes almost 35,000 houses in the city of melbourne . Few data's having [incorrect values]() and [missing values]() . This is the summary of the houses sold in city of Melbourne . Housing dataset after removing missing values and incorrect values . 

* Removed NA values
* Removed values having empty landsize and building area
* Removed values where building area exceeding land area
* Removed values of building less than eleven meters(minimum building size is
 11 meters).[REFERENCE](https://tinyhousejoy.com/2014/09/12/minimum-sizes-for-tiny-houses/)
* Removed incorrect values where date of the house was sold before the house was build

```{r echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
housing.dataset=read.csv("melbourne_data.csv") #H~1~ 
```

```{r}
housing.dataset=na.omit(housing.dataset) #Removing NA values
housing.dataset=housing.dataset[!housing.dataset$BuildingArea>housing.dataset$Landsize,] #Removing building area exceeding landsize
housing.dataset=housing.dataset[!housing.dataset$BuildingArea<11,]
datesold=as.Date(housing.dataset$Date,'%d/%m/%Y')
datesold=as.numeric(format(datesold,'%Y'))
housing.dataset["datesold"]=NA
housing.dataset$datesold=datesold
housing.dataset$datesold=as.integer(housing.dataset$datesold)
housing.dataset=housing.dataset[housing.dataset$datesold>=housing.dataset$YearBuilt,]
```

#------------------------------------------------------------------------------------

#Problem-1

Two types of houses namely townhouse and duplex are compared for their prices. Two independent samples of 500 houses were selected. Summary results were as follows:

                        townhouse               duplex

      sample size       500                     500

      sample mean       909920.4                613756.8

      sample variance   159962788568            57199360507

Using a 0.05 significance level, is there evidence that the two types of houses differ in
their mean price?

#Solution

```{r chunk_name, results="hide"}
a=housing.dataset[housing.dataset$Type=="t",] #fetching townhouses
b=housing.dataset[housing.dataset$Type=="u",] #fetching duplexes
a=a[1:500,] #fetching 500 townhouses
b=b[1:500,] #fetching 500 duplex houses
mean(a$Price) #finding mean price for townhouses
mean(b$Price) #finding mean price for duplex houses
var(a$Price) #finding variance price for townhouses
var(b$Price) #finding variance price for duplex houses
```

##1st step

Null Hypotheses->      H~0~ : u~1~ = u~2~

Alternate Hypotheses-> H~1~ : u~1~ != u~2~

##2nd step

The null hypothesis of the two-tailed test about population proportion can be expressed as 

follows:

p = p~0~
`
where p~0~ is a hypothesized value of the true population proportion p.

##3rd step

At .05 significance level

##4th step

If z > 1.96, We reject null hypotheses.

If z < -1.96, We reject null hypotheses.

##5th step

Let us calculate the test statistics

```{r echo="TRUE"}
z=(909920.4-613756.8)/sqrt((159962788568/100)+(57199360507/100))
print(z)
```

##6th step

Reject H~0~, we have sufficient evidence to conclude u~1~ != u~2~

i.e. the mean prices of two different types of houses differ

##Confidence interval

```{r echo="TRUE"}
a=(909920.4-613756.8)+(1.96)*sqrt((159962788568/100)+(57199360507/100))
b=(909920.4-613756.8)-(1.96)*sqrt((159962788568/100)+(57199360507/100))
```

204826.3 to 387500.9

We are 95% confident that the mean price of two different types of houses is between 204826.3 and 387500.9. These evidence shows us to reject the null hyotheses.

#------------------------------------------------------------------------------------

#Problem2

The real estate agent claims that the mean of landsize of houses in city of melbourne is equal or more than 607 meters. In a sample of 30 houses, it was found that the mean of those samples is 321.6 meters. Assume the standard deviation is 1128.851. At .05 significance level,can we reject the null hypotheses that the mean of landsize is lesser than 321.6 meters?

#Solution

```{r results="hide"}
a=housing.dataset
a=a[1:30,] #fetching 30 values mean of landlize
mean(a$Landsize) #finding mean
mean(housing.dataset$Landsize) #finding mean of housing.dataset
sd(housing.dataset$Landsize) #standard deviation of housing dataset
```

We can state the hypotheses as:

Null Hypotheses->      H~0~ : u >= 607

Alternate Hypotheses-> H~1~ : u < 607

##2nd step

The null hypothesis of the lower tail test of the population mean can be expressed as 

follows:

u >= u~0~
where u~0~ is a hypothesized lower bound of the true population mean u.

##3rd step

At .05 significance level

##4th step

If z < -2.58, We reject null hypotheses.

##5th step

Let us calculate the test statistics

```{r echo="TRUE"}
t=(321.6-607)/(1128.851/sqrt(30))
print(t)
```

##6th step

we fail to reject H~0~ Null hypotheses, we have sufficient evidence to conclude H~0~: u >= 607)


##critical value

We then compute the critical value at .05 significance level.

```{r echo="TRUE"}
alpha=0.05
t.alpha=qt(1-alpha,df=30-1)
print(-t.alpha)
```
The test statistic -1.384771 is greater than the critical value of -1.699127. Hence, at .05 significance level, we fail to reject the null hypotheses.

#------------------------------------------------------------------------------------

#Problem3

```{r results="hide"}
a=housing.dataset
a=a[1:40,] #fetching 40 values mean of landlize
mean(a$Car) #finding mean
mean(housing.dataset$Car) #finding mean of housing.dataset
sd(housing.dataset$Car) #standard deviation of housing dataset
```

The mean of number of car parking in the year 2016 was 1.634558. In the sample of 40 houses in the year of 2017, the mean of car parking is 1.45. At the standard deviation 0.9412223. And at significance level at .05, can we reject the null hypotheses that the mean number of car parking does not differ from last year?

#Solution

```{r results="hide"}
a=housing.dataset
a=a[1:40,] #fetching 40 values mean of landlize
mean(a$Car) #finding mean
mean(housing.dataset$Car) #finding mean of housing.dataset
sd(housing.dataset$Car) #standard deviation of housing dataset
```

We can state the hypotheses as:

Null Hypotheses->      H~0~ : u = 1.634558

Alternate Hypotheses-> H~1~ : u != 1.634558

##2nd step

The null hypothesis of the two-tailed test about population proportion can be expressed as 

follows:

p = p~0~

where p~0~ is a hypothesized value of the true population proportion p.

##3rd step

At .05 significance level

##4th step

If z > 1.96 and z < -1.96, We reject null hypotheses.

##5th step

Let us calculate the test statistics

```{r echo="TRUE"}
z=(1.45-1.634558)/(0.9412223/sqrt(40))
print(z)
```

##Critical interval

```{r echo="TRUE"}
alpha=0.05
z.half.alpha=qnorm(1-(alpha/2))
c(-z.half.alpha,z.half.alpha)
```

The test statistic -1.24014 lies between the critical values -1.959964 and 1.959964. Hence, 

at .05 significance level, we fail to reject the null hypothesis that the mean number of car 
parking does not differ from last year. 

#Alternative Solution

```{r echo="TRUE"}
pval=2*pnorm(z)
pval
```

Instead of using the critical value, we apply the pnorm function to compute the two-tailed 

p-value of the test statistic. It doubles the lower tail p-value as the sample mean is less 

than the hypothesized value. Since it turns out to be greater than the .05 significance 

level, we fail to reject the null hypothesis.

#------------------------------------------------------------------------------------

#Problem4

The price of the house on the city of melbourne have a mean of 1152201 or lesser, In a sample of 37 houses, It is found that the prices of houses are 1579838, Assume that sd is 693401.4,At 0.05 significance level ,can we reject null hypotheses?

#Solution

```{r results="hide"}
a=housing.dataset
a=a[1:37,] #fetching 37 values mean of landlize
mean(a$Price) #finding mean
mean(housing.dataset$Price) #finding mean of housing.dataset
sd(housing.dataset$Price) #standard deviation of housing dataset
```

We can state the hypotheses as:

Null Hypotheses->      H~0~ : u <= 1152201

Alternate Hypotheses-> H~1~ : u > 1152201

##2nd step

The null hypothesis of the upper tail test of the population mean can be expressed as 

follows:

u <= u~0~

where u~0~ is a hypothesized upper bound of the true population mean u.

##3rd step

At .05 significance level

##4th step

If z > 2.58, We reject null hypotheses.

##5th step

Let us calculate the test statistics

```{r echo="TRUE"}
t=(1579838-1152201)/(693401.4/sqrt(37))
print(t)
```

##6th step

Reject H~0~, we have sufficient evidence to conclude H~0~: u > 607)

i.e. the mean price is greater than population mean.

##critical value

We then compute the critical value at .05 significance level.

```{r echo="TRUE"}
alpha=0.05
z.alpha=qnorm(1-alpha)
print(z.alpha)
```
The test statistic 3.751383 is greater than the critical value of 1.644854. Hence, at .05 

significance level, we reject the null hypotheses.

#------------------------------------------------------------------------------------
